$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-02-25 paper/e6ssm-tuning-paper.tex
Added expressions for traces over U(1)' charges in terms of the E6 mixing angle, so as not to have to continuously be recalculating them when checking against the CE6SSM

\Sigma_{\tilde{Q}}=\sum_i \tilde{Q}_i^2

@@

\Sigma_{\tilde{Q}}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^Y\tilde{Q}_i,\\
\Pi_{\tilde{Q}}&=\sum_i \tilde{Q}_i^4,\\
\Pi_{\tilde{Q}}^Y&=\sum_i \left ( \sqrt{\frac{5}{3}}Q_i^Y\right )^2\tilde{Q}_i^2,\\
\Pi_{\tilde{Q}}^L&=3\tilde{Q}_1^2+3\tilde{Q}_2^2+\tilde{Q}_{H'}^2+\tilde{Q}_{\overline{H'}}^2+3\tilde{Q}_L^2+9\tilde{Q}_Q^2,\\
\Pi_{\tilde{Q}}^C&=\tilde{Q}_d^2+\tilde{Q}_D^2+\tilde{Q}_{\overline{D}}^2+2\tilde{Q}_Q^2+\tilde{Q}_u^2.

@@

Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised. Similarly we will write

@@

>>>>

\Sigma_{\tilde{Q}}=\sum_i \tilde{Q}_i^2=\frac{321}{40}\cos^2\theta+\frac{217}{24}\sin^2\theta+\frac{27}{8\sqrt{15}}\sin 2\theta

@@

\Sigma_{\tilde{Q}}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^Y\tilde{Q}_i=-\frac{3}{\sqrt{10}}\cos\theta-\frac{1}{\sqrt{6}}\sin\theta,\\
\Pi_{\tilde{Q}}&=\sum_i \tilde{Q}_i^4\\
&=\frac{2049}{1600}\cos^4\theta+\frac{483}{80\sqrt{15}}\cos^3\theta\sin\theta+\frac{681}{160}\cos^2\theta\sin^2\theta+\frac{9}{16\sqrt{15}}\cos\theta\sin^3\theta+\frac{1297}{576}\sin^4\theta,\\
\Pi_{\tilde{Q}}^Y&=\sum_i \left ( \sqrt{\frac{5}{3}}Q_i^Y\right )^2\tilde{Q}_i^2=\frac{59}{40}\cos^2\theta+\frac{31}{24}\sin^2\theta+\frac{3}{8\sqrt{15}}\sin 2\theta,\\
\Pi_{\tilde{Q}}^L&=3\tilde{Q}_1^2+3\tilde{Q}_2^2+\tilde{Q}_{H'}^2+\tilde{Q}_{\overline{H'}}^2+3\tilde{Q}_L^2+9\tilde{Q}_Q^2=\frac{39}{20}\cos^2\theta+\frac{19}{12}\sin^2\theta+\frac{3}{4\sqrt{15}}\sin 2\theta,\\
\Pi_{\tilde{Q}}^C&=\tilde{Q}_d^2+\tilde{Q}_D^2+\tilde{Q}_{\overline{D}}^2+2\tilde{Q}_Q^2+\tilde{Q}_u^2=\frac{1}{2}.

@@

Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised. The expressions in terms of the $E_6$ mixing angle $\theta$ follow from the charge assignments given in Table \ref{tab:E6charges} and hold provided that $U(1)$ mixing is neglected. Similarly we will write

@@

If the one-loop contributions to the effective potential from top and stop loops are also included it is necessary to consider the expansions for $y_t$, $a_t$, $m_{Q3}^2$ and $m_{u3}^2$. The necessary expressions for $y_t$ read
\beta_{y_t}^{(1)}&=y_t\left [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2-2g_1'^2\left ( \tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_u^2 \right )\right ],\label{eq:USSMYu22BetaOneLoop}\\
\beta_{y_t}^{(2)}&=,\label{eq:USSMYu22BetaTwoLoop}\\
b_{y_t}^{(2)}&=,\label{eq:USSMYu22Ot2Coeff}
and those for $a_t$ read
\beta_{a_t}^{(1)}&=,\label{eq:USSMTYu22BetaOneLoop}\\
\beta_{a_t}^{(2)}&=,\label{eq:USSMTYu22BetaTwoLoop}\\
b_{a_t}^{(2)}&=.\label{eq:USSMTYu22Ot2Coeff}
The one- and two-loop $\beta$ functions and the resulting $O(t^2)$ coefficient for $m_{Q3}^2$ are 
\beta_{m_{Q3}^2}^{(1)}&=,\label{eq:USSMmq222BetaOneLoop}\\
\beta_{m_{Q3}^2}^{(2)}&=,\label{eq:USSMmq222BetaTwoLoop}\\
b_{m_{Q3}^2}^{(2)}&=.\label{eq:USSMmq222Ot2Coeff}
Finally, the relevant expressions for the soft mass $m_{u3}^2$ read
\beta_{m_{u3}^2}^{(1)}&=,\label{eq:USSMmu222BetaOneLoop}\\
\beta_{m_{u3}^2}^{(2)}&=,\label{eq:USSMmu222BetaTwoLoop}\\
b_{m_{u3}^2}^{(2)}&=.\label{eq:USSMmu222Ot2Coeff}
